Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-28 paper/EDA.qmd
Adding Assumtion graph Time Take in Second for Game for before and after Taking drug

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Assumption Check for Time taken before taking the Drug"

# Fit ANOVA Model
model_b <- aov(game_before ~ drug, data = clean_data)

# Check Model Assumptions
check_model(model_b, check = c("normality", "homogeneity"))
```
